---
title: "Title of your project"
author:
- familyname: your last name
  othernames: your first name
  title: Prof./Dr./Mr./Ms./
  qualifications: MSc in Logistics and Operations Management(edit if required)
  correspondingauthor: true
department: Cardiff Business School\newline Logistics &\newline Operations Management
email: your_email@cardiff.ac.uk
id: 0740028082 #your student ID
organization: Cardiff Business School
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
header-includes:  
 \usepackage{float} #use the 'float' package
output:
  bookdown::pdf_document2:
    template: cardiffcoursework.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    number_sections: yes
    citation_package: biblatex
    toc: true
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE,fig.pos = 'H')
# Make sure you have the latest versions of rmarkdown and bookdown installed
library(tidyverse)
library(fpp3)
```


# Introduction {#intro}

in section \@ref(intro), you can provide an overview of the coursework.

In a famous paper, @BC64 and @makridakis2000m3 introduced a family of transformations \dots

```{r histogram,  fig.cap="better graph", message=FALSE, warning=FALSE}
qplot(exp(rnorm(200)))
```

Consider the logNormal data plotted in Figure \@ref(fig:histogram).

# Part A


\begin{equation}
\bar{X} = \frac{\sum_{i=1}^n X_i}{n} (\#eq:mean)
\end{equation}


In Equation \@ref(eq:mean)

You can use the following if you want equations without numbers.

$$s^2 = \sum_{i=1}^n (x_i-\bar{x})^2$$

# Part B

In this part, we will consider:

```{r mtcars, fig.cap="", out.extra=""}
knitr::kable(head(mtcars, 10), caption = "this table.")
```

see Table \@ref(tab:mtcars). 

# Part C


# Part D

# References
